Classical density functional theory for the square-well liquid

### 2014-07-01 papers/square-well-liquid/paper.tex

\newcommand\xx{\mathbf{x}}
\newcommand\rr{\mathbf{x}}
\newcommand\fixme[1]{\textcolor{red}{\textbf{[#1]}}}

@@

\begin{multline}
  g_S(r,g_\sigma) = 1 + (g_\sigma-1) e^{-\kappaO \left(\frac{r}{\sigma}-1\right)} \\
  + (g_\sigma -1)(\kappaO - 2g_\sigma)  \left(\frac{r}{\sigma}-1\right)e^{-\kappaI  \left(\frac{r}{\sigma}-1\right)} \\
  + I(g_\sigma)  \left(\frac{r}{\sigma}-1\right)^2e^{-\kappaZ  \left(\frac{r}{\sigma}-1\right)}
\end{multline}
\begin{equation}
  I(g_\sigma) = \kappaZ^5 \frac{
    \frac{\chi-1}{24\eta} + (1-g_\sigma) \frac{(\kappaO-2
      g_\sigma)(\kappaI^2 + 4 \kappaI + 6)}{\kappaI^4}
    + (1-g_\sigma)\frac{\kappaO^2 + 2\kappaO + 2}{\kappaO}
  }{2 \kappaZ^2 + 12 \kappaZ + 24}
\end{equation}
\begin{equation}
  \chi = \frac{(1-\eta)^4}{\eta^4 - 4\eta^3 + 4\eta^2 + 4\eta + 1}
\end{equation}
Finally, we can convert between the packing fraction $\eta$ and the
radial distribution function at contact $g_\sigma$ using the
Carnahan-Starling approximation for $g_\sigma$:
\newcommand\nastyetacuberoot{\sqrt[3]{54 g_\sigma^2 -
    6\sqrt{81g_\sigma^4 - 6g_\sigma^3}}}
\begin{align}
  g_\sigma &= \frac{1-\tfrac{\eta}{2}}{(1-\eta)^3}\text{, and its inverse} \\
  \eta &= 1 - \frac{1}{\nastyetacuberoot} - \frac{\nastyetacuberoot}{6g_\sigma}.
\end{align}
This function includes three fitted parameters, $\kappaO =
\kappazero$, $\kappaI = \kappaone$,
and $\kappaZ = \kappatwo$.

\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}

>>>>

\newcommand\kk{\mathbf{k}}
\newcommand\xx{\mathbf{x}}
\newcommand\rr{\mathbf{r}}
\newcommand\fixme[1]{\textcolor{red}{\textbf{[#1]}}}

@@

\begin{multline}\label{eq:gs}
  g_S(r,g_\sigma) = 1 + (g_\sigma-1) e^{-\kappaO \left(\frac{r}{\sigma}-1\right)} \\
  + (g_\sigma -1)(\kappaO - 2g_\sigma)  \left(\frac{r}{\sigma}-1\right)e^{-\kappaI  \left(\frac{r}{\sigma}-1\right)} \\
  + I(g_\sigma)  \left(\frac{r}{\sigma}-1\right)^2e^{-\kappaZ  \left(\frac{r}{\sigma}-1\right)}
\end{multline}
\begin{equation}
  I(g_\sigma) = \kappaZ^5 \frac{
    \frac{\chi-1}{24\eta} + (1-g_\sigma) \frac{(\kappaO-2
      g_\sigma)(\kappaI^2 + 4 \kappaI + 6)}{\kappaI^4}
    + (1-g_\sigma)\frac{\kappaO^2 + 2\kappaO + 2}{\kappaO}
  }{2 \kappaZ^2 + 12 \kappaZ + 24}
\end{equation}
\begin{equation}
  \chi = \frac{(1-\eta)^4}{\eta^4 - 4\eta^3 + 4\eta^2 + 4\eta + 1}
\end{equation}
Finally, we can convert between the packing fraction $\eta$ and the
radial distribution function at contact $g_\sigma$ using the
Carnahan-Starling approximation for $g_\sigma$:
\newcommand\nastyetacuberoot{\sqrt[3]{54 g_\sigma^2 -
    6\sqrt{81g_\sigma^4 - 6g_\sigma^3}}}
\begin{align}
  g_\sigma &= \frac{1-\tfrac{\eta}{2}}{(1-\eta)^3}\text{, and its inverse} \\
  \eta &= 1 - \frac{1}{\nastyetacuberoot} - \frac{\nastyetacuberoot}{6g_\sigma}.
\end{align}
This function includes three fitted parameters, $\kappaO =
\kappazero$, $\kappaI = \kappaone$,
and $\kappaZ = \kappatwo$.

\subsubsection{Fourier transform of radial distribution function}

\newcommand\kapovsig[1]{\frac{\kappa_{#1}}{\sigma}}

For or purposes, we want to Fourier transform $g_s(r,g_\sigma)u_{SW}(\rr)$ and
the square well potential since it is used in the free energy functional.
\begin{align}
  \tilde{g_s}(k, g_\sigma) =\int^\infty_{-\infty} g_s(r, g_\sigma)u_{SW}(\rr)e^{-i\kk \cdot \rr}\mathrm{d}^3\rr
\end{align}
Since the radial distribution function and potential are radially symmetric, we can
express the dot product differently so that the transform is
\begin{align}
  \tilde{g_s}(k, g_\sigma) &=\int^\infty_{-\infty} g_s(r,
  g_\sigma)u_{sw}(r)e^{-ikr \cos \theta}\mathrm{d}^3\rr \\
  &= 2 \pi \int_\sigma^{\lambda \sigma} \int_0^\pi g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \sin \theta \, \mathrm{d}r \mathrm{d}\theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} \int_{1}^{-1} g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \mathrm{d}r \mathrm{d}\cos \theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} g_s(r, g_\sigma) \frac{1}{-ikr}\bigg[e^{ikr} -
    e^{-ikr} \bigg]r^2 \mathrm{d}r \\
 &= \frac {4\pi}{k}\int_\sigma^{\lambda \sigma} r g_s(r,g_\sigma) \sin (kr) \mathrm{d}r.
\end{align}
Now I'll do the separate integrals for each part on the right hand
side of Eqn. \ref{eq:gs}. The first term is 1, so we are left with
a delta function.  We will ignore this term, and
move onto the next one whose integral is
\begin{align}
  \int_\sigma^{\lambda \sigma}r(g_\sigma -1) e^{-\kappa_0
    \left( \frac{r}{\sigma}-1 \right)} \sin(kr)\mathrm{d}r.
\end{align}
If we pull out constants and put this into Mathematica,
\begin{widetext}
  \begin{align}
  \int_\sigma^{\lambda
    \sigma}re^{-\frac{\kappa_0}{\sigma}r}\sin(kr)\mathrm{d}r
  &= \frac{1}{(k^2 + (\kapovsig{0})^2)^2} \bigg\{ e^{-\kappaO} \left[k
      \left(2\kapovsig{0} + \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\sigma k) + \left((\kapovsig{0})^2(1 + \kappaO) +
      k^2(\kappaO-1)\right) \sin (\sigma k) \right] \notag \\
  &- e^{-\lambda
    \kappaO} \left[ k
      \left(2\kapovsig{0} + \lambda \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\lambda \sigma k) + \left((\kapovsig{0})^2(1 + \lambda \kappaO) +
      k^2(\lambda\kappaO-1)\right) \sin (\lambda \sigma k)\right] \bigg\}
  \end{align}
\end{widetext}
\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}
